Memory-efficient Mixed-Precision Implementations for\\Robust Explicit MPC

### 2019-04-07 emsoft-2019/RMPC_Daisy.tex
updates

\section{Robust MPC and Finite Precision}
\subsection{Robust Explicit MPC}
\def\reals{\mathbb{R}}
We consider class of discrete time linreat time invariant systems
\begin{equation}
\label{eq:DSS}
x_{k+1}=Ax_k+Bu_k+Ew_k
\end{equation}
where, $x\in \reals^{n\times 1}$ is state vector, $u\in \reals^{m\times 1}$ the control input vector, $w\in \reals^{d\times 1}$ the disturbance vector, $A\in \reals^{n\times n}$ the state matrix, $B\in \reals^{n\times m}$ the input matrix, $E\in \reals^{n\times d}$, $k$ the time instant and the pair $(A,B)$ is stablizable. Knowing that $w\in\mathcal{W}$, where $\mathcal{W}$ is a polyhedral set, we try to solve for the following optimization problem:
\begin{align}
\label{eq:RMPC_prob}
\min_{u_0,\cdots,u_{N-1}}\max_{w_0,\cdots,w_{N-1}}& x_N^TQ_Fx_N+\sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i)\nonumber\\
\text{s.t.}\quad\forall i\in\{0,1,\cdots,&N-1\}:\nonumber\\
&x_{i+1}=Ax_i+Bu_i\nonumber\\
&x_i\in\mathcal{X},\quad u_i\in \mathcal{U}	
\end{align}
where, $\mathcal U$ and $\mathcal X$ are polyhedral sets, $Q\in\reals^{n\times n}$, $R\in\reals^{m\times m}$ and $Q_F\in\reals^{n\times n}$ are positive semidefinite matrices and $N$ denotes the length of prediction horizon. By making use of the fact that $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$, one can translate \eqref{eq:RMPC_prob} into a multi-parametric quadratic problem which admits a closed-form solution $U_N=K(x_0)$. Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $K$ is a continuous piecewise affine (PWA) function over polydedral regions:
\begin{equation}
K(x_k)=
\begin{cases}
F_1x_k+G_1 & \text{if $x_k\in \mathcal{R}_1$}\\
F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
\vdots\\
F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
\end{cases} 
\end{equation}
where $\mathcal{R}_i$ is a ploytob determined by  a set of linear inequalities $H_ix\leq K_i$. To find the controller $K$ we rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}. We call \statespace\space the union of all regions $X_{i}$ in the domain of the state variable $x_{k}$:
\begin{equation}
\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
\end{equation}
Therefore, given the state vector $x$, to compute control input, one has to first determine to which polytope does the state vector belong. Several algorithms are proposed to solve for this problem [references?]. This work does not rely on any specific technique to verify which region \statevarmath belongs to, so we consider a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.

>>>>

\section{Robust MPC and Finite Precision}
\subsection{Robust Explicit MPC}
\def\reals{\mathbb{R}}
We consider class of discrete time linreat time invariant systems
\begin{equation}
\label{eq:DSS}
x_{k+1}=Ax_k+Bu_k+Ew_k
\end{equation}
where, $x\in \reals^{n\times 1}$ is state vector, $u\in \reals^{m\times 1}$ the control input vector, $w\in \reals^{d\times 1}$ the disturbance vector, $A\in \reals^{n\times n}$ the state matrix, $B\in \reals^{n\times m}$ the input matrix, $E\in \reals^{n\times d}$, $k$ the time instant and the pair $(A,B)$ is stablizable. Knowing that $w\in\mathcal{W}$, where $\mathcal{W}$ is a polyhedral set, we try to solve for the following optimization problem:
\begin{align}
\label{eq:RMPC_prob}
\min_{u_0,\cdots,u_{N-1}}\max_{w_0,\cdots,w_{N-1}}& x_N^TQ_Fx_N+\sum_{i=0}^{N-1}(x_i^TQx_i+u_i^TRu_i)\nonumber\\
\text{s.t.}\quad\forall i\in\{0,1,\cdots,&N-1\}:\nonumber\\
&x_{i+1}=Ax_i+Bu_i\nonumber\\
&x_i\in\mathcal{X},\quad u_i\in \mathcal{U}	
\end{align}
where, $\mathcal U$ and $\mathcal X$ are polyhedral sets, $Q\in\reals^{n\times n}$, $R\in\reals^{m\times m}$ and $Q_F\in\reals^{n\times n}$ are positive semidefinite matrices and $N$ denotes the length of prediction horizon. By making use of the fact that $x_i=A^ix_0+\sum_{l=0}^{i-1}A^{i-l-1}Bu_l$, one can translate \eqref{eq:RMPC_prob} into a multi-parametric quadratic problem which admits a closed-form solution $U_N=K(x_0)$. Furthermore, for the case that $Q\geq0$, $Q_F\geq0$ and $R>0$, the controller $K$ is a continuous piecewise affine (PWA) function over polydedral regions:
\begin{equation}
K(x_k)=
\begin{cases}
F_1x_k+G_1 & \text{if $x_k\in \mathcal{R}_1$}\\
F_2x_k+G_2 & \text{if $x_k\in \mathcal{R}_2$}\\
\vdots\\
F_Px_k+G_P & \text{if $x_k\in \mathcal{R}_P$}
\end{cases} 
\end{equation}
where $\mathcal{R}_i$ is a ploytob determined by  a set of linear inequalities $H_ix\leq K_i$. To find the controller $K$ we rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}. We call \statespace\space the union of all regions $X_{i}$ in the domain of the state variable $x_{k}$:
\begin{equation}
\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
\end{equation}
Therefore, given the state vector $x$, to compute control input, one has to first determine to which polytope does the state vector belong. Several algorithms are proposed to solve for this problem [references?]. The simplest technique to verify which region \statevarmath belongs to is to make a linear search over all the regions in \statespace\space, using a case-of conditional statement similar to the one in Listing \ref{lst:caseof}.
